A comparison of approaches to Kazakh to Kyrgyz machine translation

### 2015-02-19 2015-eamt-kazkir/2015-eamt-kazkir.tex
harg
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59007 72bbbca6-d526-0410-a7d9-f06f51895060
more
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59008 72bbbca6-d526-0410-a7d9-f06f51895060
lll
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59009 72bbbca6-d526-0410-a7d9-f06f51895060
hargle
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59018 72bbbca6-d526-0410-a7d9-f06f51895060
stuff
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59025 72bbbca6-d526-0410-a7d9-f06f51895060

>>>>

\section{Kazakh and Kyrgyz}

\section{Approaches}

\subsection{Rule-based machine translation}

\cite{washingtonsalimzyantyers14}
\cite{washingtonipasovtyers12}

\subsection{Corpus-based machine translation}

We trained models based on two approaches, the first being phrase-based machine translation (PBMT, \cite{zens2002}) and the second on character-based machine translation (CBMT, \cite{nakov2012}; \cite{TiedemannEAMT2009}).

\subsection{Corpus}

\subsubsection{Phrase-based}

\subsubsection{Character-based }

\cite{nakov2012} present a method of statistical machine translation on the character level between related languages that takes advantage of phrase-based machine translation architecture. 
%The method relies on preprocessing the input and output by inserting spaces in between the characters of words, for example the string `m\"{a} meen Helsinkiin' would become `m \"{a} \$ m e e n \$ H e l s i n k i i n' with a unigram model, or `m\"{a} \"{a}\$ \$m me ee en n\$ \$H He el ls si in nk ki ii in' with a bigram model.

%After preprocessing, the corpora are processed as with the phrase-based system, with the difference that the language model order is increased from 5 to 10-grams.

\section{Evaluation}

\subsection{Coverage}

\begin{table}
  \begin{tabular}{|l|r|r|r|r|}
    \hline
    \textbf{Corpus} & \textbf{Tokens} & \textbf{RBMT} & \textbf{PBSMT} & \textbf{CBMT} \\
    \hline
    NT              & 144,946      &      &          &       \\
    Akorda          & 382,716       &      &          &       \\
    Wikipedia       & 27,802,493       &      &          &       \\
    \hline
  \end{tabular}
  \caption{Vocabulary coverage for the three systems}
  \label{table:coverage}
\end{table}

\subsection{Translation quality}

\section{Future work}

\section{Conclusions}
